A Dissection of Foregrounds in Epoch of Reionization Observations from the Murchison Widefield Array

### 2015-01-21 ms.tex
Shorten sentence in summary on baseline screening
In ms.tex,

(*) Shorten a sentence in the summary on baseline screening

We also provide a simple and effective tool based on the delay spectrum technique {\bf that can potentially} mitigate foreground contamination by {\bf nearly two orders} of magnitude in EoR data analysis by discarding or down--weighting data from antenna pairs most affected by foreground contamination as a function of antenna spacing vector and time of observation, with negligible loss of sensitivity. In conclusion, we find that inclusion of emission models, both diffuse and compact, all the way to the horizon is essential to explaining the observed power spectrum.

>>>>

We also provide a simple and effective tool based on the delay spectrum technique {\bf that can potentially} mitigate foreground contamination by {\bf nearly two orders} of magnitude in EoR data analysis by discarding or down--weighting data from antenna pairs most affected by foreground contamination, with negligible loss of sensitivity. In conclusion, we find that inclusion of emission models, both diffuse and compact, all the way to the horizon is essential to explaining the observed power spectrum.
